---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.pos = 'H')

library(magrittr)
library(ggplot2)

library(colorspace)
library(pals)
library(scales)
library(unikn)


# forces a line before and after each plot
# https://stackoverflow.com/questions/37030219/r-markdown-plots-within-a-loop-going-out-of-margin-when-typesetting-to-pdf
my_plot_hook <- function(x, options)
  paste("\n", knitr::hook_plot_tex(x, options), "\n")
knitr::knit_hooks$set(plot = my_plot_hook)

fig1_url <- "http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/figure/unnamed-chunk-7-1.png"

```





# Color Palettes

## Palettes collection

### Qualitative

#### Freestyle

```{r}

# Color Brewer sequence 1: red blue green purple orange

list(
    set1 = c("#DE5262", "#3082A7", "#529E3A", "#7B68AB", "#F28B46"),
    set1_hcl = c('#E05365', '#3B8CB3', '#43951D', '#956DE5', '#CD6803')
    
) %>% seecol()

list(
    set1 = c("#EC3745", "#4984D7", "#4CBA80", "#9D538D", "#F28933"),
    set1_hcl = c('#FF525E', '#3392FB', '#0AA567', '#EA52CE', '#DA7706')
    
) %>% seecol()

list(
    set1 = c("#EA3546", "#008FF7", "#1BBC52", "#BA53A5", "#E7A000")
) %>% seecol()


c('#25A37C', '#FDB304', '#12ACE6', '#FB5379', '#C08361') %>% seecol()

c('#FA5284', '#3494EE', '#DE59E0', '#899906', '#FEB312') %>% seecol()

c('#EF4067', '#3F89C5', '#B75CDC', '#34963B', '#F5812F') %>% seecol()

```

#### Free as ColorBrewer

		        Dark2	H	C	L	Set2	H	C	L
1	blue-green	#1b9e77	155	52	58	#66c2a5	162	44	72
2	orange	    #d95f02	26	113	57	#fc8d62	26	95	70
3	violet	    #7570b3	268	56	50	#8da0cb	253	41	66
4	pink	    #e7298a	349	115	52	#e78ac3	331	60	69
5	green	    #66a61e	115	76	62	#a6d854	108	81	81
6	yellow	    #e6ab02	57	90	74	#ffd92f	69	95	87
7	brown	    #a6761d	52	64	53	#e5c494	57	45	81
8	grey	    #666666	94	0	43	#b3b3b3	94	0	73
				                55					72
									
		        Set1				Pastel1			
1	red	        #e41a1c	12	152	49	#fbb4ae	17	49	80
2	blue	    #377eb8	244	62	51	#b3cde3	236	25	81
3	green	    #4daf4a	127	74	64	#ccebc5	121	30	90
4	purple	    #984ea3	301	63	45	#decbe4	298	20	84
5	orange	    #ff7f00	30	122	67	#fed9a6	56	48	89
6	yellow	    #ffff33	86	103	97	#ffffcc	86	37	99
7	brown	    #a65628	29	72	46	#e5d8bd	67	24	87
8	pink	    #f781bf	339	75	69	#fddaec	333	21	90
                                60                  88

```{r}

RColorBrewer::brewer.pal(8, "Dark2") %>% seecol()

c('#E51C1F', '#1D98B0', '#80AF21', '#BC5A96', '#FB723A', '#E4FA2A', '#A98B07', '#F879AC') %>% seecol()

```




### Sequential

```{r}

colorspace::hcl_palettes("sequential (single-hue)", n = 9, plot = TRUE)
colorspace::hcl_palettes("sequential (multi-hue)", n = 9, plot = TRUE)

RColorBrewer::brewer.pal.info %>% 
  .[.$category == "seq", ] %>%
    tibble::rownames_to_column(var = "palette") %>%
    apply(., 1, function (x) {
        n <- as.numeric(x["maxcolors"])
        pal_name <- as.character(x["palette"]) 
        RColorBrewer::brewer.pal(n, pal_name) %>% usecol() %>% 
            `comment<-`(paste(pal_name))
    }) %>% t() %>% split(1:nrow(.)) %>%
    `names<-`(rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "seq"]) 

```

### Diverging

```{r}

colorspace::hcl_palettes("diverging", n = 11, plot = TRUE)

```




## Custom HCL Palettes

```{r}

# sequence as in ColorBrewer: qual Set2
# red blue green purple orange yellow brown 
# sample in coolors.co

c("#f33d4b", "#2f6690", "#1b998b", "#aa5c95", "#ff7733", "#ffc914", "#e28413") %>% seecol()
c("#F6514C", "#2e86ab", "#44af69", "#aa45e0", "#fe9920", "#f5d547", "#ba9b21") %>% seecol()

```


```{r}


# yellow gold
# orange gold
# cyan

list(
    fivethirtyeight1 = c('#EB6A10', '#23A1B9', '#8048ED', '#E60CAD', '#666666'),
    fivethirtyeight1_hcl = c('#EC6A0A', '#0A9FB7', '#9F79FE', '#FD3EC1', '#919191')
) %>% seecol()

list(
  
  jcolors_default = c('#2FBC26', '#1BA5CC', '#FE7B7B', '#9C98FE', '#D19A0A'),
  jcolors_pal2 = c('#38A3FC', '#8BA90F', '#FA61DD', '#FE743E', '#08B19F'),
  jcolors_pal3 = c('#5AB204', '#15AADE', '#FE7263', '#CB7CFC', '#AEA00B'),
  munsell_5pure = c('#1496AF', '#FE3B57', '#0D9C6F', '#C25CE7', '#A08705'),
  munsell_10pure = c('#1685B2', '#DB4C06', '#038C74', '#CD3FBA', '#837F0C'),
  munsell_5mix = c('#0F8EF2', '#D1740C', '#0F9C93', '#F148A1', '#7B960C'),
  munsell_10mix = c('#16A3AB', '#C2890E', '#A47BFE', '#09AB23', '#FF5487'),
  beach_toys = c('#2E8AFD', '#4D9E10', '#DC58BF', '#B38407', '#E6623F'),
  garden_variety = c('#0082B2', '#90780B', '#8B67C5', '#018C4D', '#CA5062'),
  kids_party = c('#F2AC05', '#F099FE', '#60D109', '#FF9CB5', '#20C8FA'),
  summerset = c('#7E90FE', '#20B02F', '#F559D8', '#E28007', '#FC695D'),
  dusk = c('#6575A9', '#8F7405', '#B06060', '#448456', '#797675'),
  mango_tango = c('#FF8D47', '#1CB8F0', '#D8A301', '#FD77F5', '#4AC345'),
  lavender_dream = c('#4E598C', '#745817', '#05647E', '#90454E', '#106948'),
  scientific_report = c('#AB3E3E', '#0067A7', '#815D09', '#6D4DC3', '#2E7A0A'),
  graph_viz = c('#1DA9A9', '#E17F42', '#C379F1', '#81A503', '#EB7570'),
  flat_mate = c('#5379A8', '#9D6D2B', '#278664', '#BE5844', '#797774'),
  something = c('#AC8705', '#5B88EE', '#419C1D', '#EA4CB2', '#E3644D'),
  something = c('#7C757C', '#B76013', '#158938', '#656ADF', '#1981A2'),
  awesome_red = c('#FF1F56', '#44960E', '#6975FE', '#F208C3', '#C740FD'),
  something = c('#AD0353', '#356206', '#2145D8', '#864705', '#A92103'),
  carrot_day = c('#E95B2D', '#4884FB', '#B28008', '#F54184', '#209E34'),
  something = c('#51AC43', '#CE76E0', '#D18909', '#6896F9', '#F96597'),
  something = c('#AB4565', '#4D7229', '#5D5DBE', '#945A2B', '#67676F'),
  fading_away = c('#95B664', '#9AA8EA', '#E09D64', '#50BDA4', '#EC90AB'),
  something = c('#719355', '#B072BD', '#429781', '#D26C50', '#538EC0'),
  something <- c('#2E9ACF', '#D37B27', '#F152B6', '#65A028', '#F8596E'),
  npg_hcl = c('#FE6D58', '#18A9CC', '#03B08C', '#DE870E', '#99A202'),
  jungle = c('#2C9C81', '#E96026', '#3492CF', '#B78215', '#7E921E'),
  something = c('#A63B07', '#592FFD', '#486806', '#AD0B94', '#BD043E'),
  volcano = c('#C26F10', '#5779FD', '#529410', '#EA0EDC', '#FD2361'),
  baby_girl = c('#EEBA0B', '#75D90A', '#F9A2FE', '#1CD9B7', '#37D1FB'),
  fluo_light = c('#F4E316', '#FAD3FE', '#8AFB1E', '#FFDB96', '#20FDBC'),
  something = c('#A93C96', '#267550', '#B93D30', '#326C9E', '#736923'),
  something = c('#F266B0', '#37AC6E', '#F37152', '#499CF3', '#AD982C'),
  something = c('#63BEFD', '#E6AD15', '#B4B6B8', '#73CC0F', '#FE9A9E'),
  something = c('#36A0E3', '#C39022', '#97999A', '#64AA28', '#E97679'),
  royal_family = c('#A42208', '#01622E', '#9C0B86', '#923805', '#0D4C8A')
    
) %>% seecol()


# #0066a7, #a2c7df, #f5f5e6
# #f5f5e6, #e0b9b9, #ac3f3f
c('#0066a7', '#4b81b7', '#759dc6', '#9ebad4', '#c8d8df', '#f5f5e6', '#e9d0c7', '#ddaca6', '#cf8883', '#be6561', '#ac3f3f') %>% seecol()




```


```{r}

list(
  c('#4e8273', '#598f80', '#659c8e', '#73a99b', '#81b6a9', '#92c3b7', '#a4d0c5', '#b7ddd4', '#cde9e2', '#e5f4f0', '#ffffff'),
  c('#002a33', '#103d4a', '#255060', '#3d6474', '#557987', '#6f8e98', '#8aa4a9', '#a6bab8', '#c3d1c6', '#e1e8d4', '#ffffe0'),
  sci_reports_1 = c('#ac3f3f', '#bd625e', '#cb837d', '#d8a49d', '#e1c5bc', '#e8e8d7', '#bcced6', '#95b3ce', '#6f99c3', '#477fb6', '#0066a7'),
  sci_reports_2 = c('#00abab', '#49b9b8', '#70c6c4', '#94d3cf', '#badfd6', '#e8e8d7', '#ecd0b7', '#ebb896', '#e6a276', '#df8b56', '#d67535'),
  jpr_theme = c('#1952a5', '#20639f', '#227596', '#218688', '#159873', '#4fa551', '#8cac36', '#bfb02b', '#f1b034')
) %>% seecol()

```


### Random palettes

```{r}

ggthemes::calc_pal()(10) %>%
{ . ->> tmp } %>%
    scales::show_col()

tmp %>% 
    colorspace::hex2RGB() %>%
    as(., "polarLUV") %>% .@coords %>% 
    .[order(.[,1]), ]
    round(0)

```



### HCL palettes

http://colorspace.r-forge.r-project.org/articles/hcl_palettes.html


```{r}

# HCL palettes
hcl.pals()
colorspace::hcl_palettes()

colorspace::hcl_palettes("qualitative", n = 7, plot = TRUE)
colorspace::hcl_palettes("sequential (single-hue)", n = 7, plot = TRUE)
colorspace::hcl_palettes("sequential (multi-hue)", n = 7, plot = TRUE)
colorspace::hcl_palettes("diverging", n = 7, plot = TRUE)

```

### ColorBrewer Palettes

```{r}

# RColorBrewer
# RColorBrewer::display.brewer.all()


rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "qual"] %>% 
    `names<-`(paste0("pal", 1:length(.)))
RColorBrewer::brewer.pal.info %>% 
  .[.$category == "qual", ] %>%
    tibble::rownames_to_column(var = "palette") %>%
    apply(., 1, function (x) {
        n <- as.numeric(x["maxcolors"])
        pal_name <- as.character(x["palette"]) 
        RColorBrewer::brewer.pal(n, pal_name) %>% usecol() %>% 
            `comment<-`(paste(pal_name))
    }) %>% 
    `names<-`(rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "qual"]) %>%
    unikn::seecol(., col_brd = "white", lwd_brd = 4, 
                  title = "ColorBrewer palettes - qualitative")


rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "seq"] %>% 
    `names<-`(paste0("pal", 1:length(.)))
RColorBrewer::brewer.pal.info %>% 
  .[.$category == "seq", ] %>%
    tibble::rownames_to_column(var = "palette") %>%
    apply(., 1, function (x) {
        n <- as.numeric(x["maxcolors"])
        pal_name <- as.character(x["palette"]) 
        RColorBrewer::brewer.pal(n, pal_name) %>% usecol() %>% 
            `comment<-`(paste(pal_name))
    }) %>% t() %>% split(1:nrow(.)) %>%
    `names<-`(rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "seq"]) %>%
    unikn::seecol(., col_brd = "white", lwd_brd = 4, 
                  title = "ColorBrewer palettes - sequential")

rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "div"] %>% 
    `names<-`(paste0("pal", 1:length(.)))
RColorBrewer::brewer.pal.info %>% 
  .[.$category == "div", ] %>%
    tibble::rownames_to_column(var = "palette") %>%
    apply(., 1, function (x) {
        n <- as.numeric(x["maxcolors"])
        pal_name <- as.character(x["palette"]) 
        RColorBrewer::brewer.pal(n, pal_name) 
    }) %>% t() %>% split(1:nrow(.)) %>%
    `names<-`(rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "div"]) %>%
    unikn::seecol(., col_brd = "white", lwd_brd = 4, 
                  title = "ColorBrewer palettes - divergent")
```

### Viridis Palettes

Viridis palettes are included in HCL palettes

```{r, eval=FALSE}

# Viridis
library(viridis)
c1 <- viridis(12)
c2 <- magma(12)
c3 <- inferno(12)
c4 <- plasma(12)
c5 <- cividis(12)
unikn::seecol(list(c1, c2, c3, c4, c5), col_brd = "white", lwd_brd = 4,
title = "Various viridis color palettes (n = 20)")

```

### ggthemes palettes

```{r}

ggthemes::ggthemes_data %>% names()

pal_name <- "solarized"

tmp <- ggthemes::ggthemes_data %>% .[[pal_name]] %>% lapply(., "[", "value") %>% lapply(is.data.frame) %>% unlist()
ggthemes::ggthemes_data %>% .[[pal_name]] %>% lapply(., "[", "value") %>% .[tmp] %>% lapply(t) %>% 
    seecol(title = paste0("ggthemes ", pal_name, " palettes"))


pal_name <- "ptol"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% .[[1]] %>%
    seecol(title = paste0("ggthemes ", pal_name, " palettes"))

pal_name <- "calc"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% .[["colors"]] %>% .$value %>%
    seecol(title = paste0("ggthemes ", pal_name, " palettes"))


pal_name <- "tableau"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% .$'color-palettes' %>% 
    .$regular %>% lapply("[", "value") %>% lapply(t) %>% 
    seecol(title = paste0("ggthemes ", pal_name, " regular palettes"))

ggthemes::ggthemes_data %>% .[[pal_name]] %>% .$'color-palettes' %>% 
    .$'ordered-diverging' %>% lapply("[", "value") %>% lapply(t) %>% 
    seecol(title = paste0("ggthemes ", pal_name, " ordered-diverging palettes"))


ggthemes::ggthemes_data %>% .[[pal_name]] %>% .$'color-palettes' %>% 
    .$'ordered-sequential' %>% lapply("[", "value") %>% lapply(t) %>% 
    seecol(title = paste0("ggthemes ", pal_name, " ordered-sequential palette"))


pal_name <- "few"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% .$colors %>%
    lapply("[", "value") %>% lapply(t) %>% 
    seecol(title = paste0("ggthemes ", pal_name, " palette"))

pal_name <- "manyeyes"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% 
    seecol(title = paste0("ggthemes ", pal_name, " palette"))

pal_name <- "gdocs"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% .$colors %>%
    seecol(title = paste0("ggthemes ", pal_name, " palette"))



```


### ggsci palettes

```{r}

library(ggsci)

c("NPG", "AAAS", "NEJM", "Lancet", "JAMA", "JCO", "LocusZoom") %>%
    `names<-`(paste0("pal", 1:length(.)))

list(
    pal_npg("nrc")(10),
    pal_aaas("default")(10),
    pal_nejm("default")(8),
    pal_lancet("lanonc")(9),
    pal_jama("default")(7),
    pal_jco("default")(10),
    pal_locuszoom("default")(7)
) %>%
    seecol(., col_brd = "white", lwd_brd = 2, 
           title = "ggsci palettes")


c("D3.20", "D3.20b",  "D3.20c") %>%
    `names<-`(c("pal1-2", "pal3-6", "pal7-11"))

list(
    pal_d3("category20")(20)[1:10],
    pal_d3("category20")(20)[11:20],
    pal_d3("category20b")(20)[1:5],
    pal_d3("category20b")(20)[6:10],
    pal_d3("category20b")(20)[11:15],
    pal_d3("category20b")(20)[16:20],
    pal_d3("category20c")(20)[1:5],
    pal_d3("category20c")(20)[6:10],
    pal_d3("category20c")(20)[11:15],
    pal_d3("category20c")(20)[16:20]
) %>%
    seecol(., col_brd = "white", lwd_brd = 2, 
           title = "ggsci D3 palettes")

```


### pals bivariate palettes

```{r}

# Discrete
# pal.bands(alphabet, alphabet2, cols25, glasbey, kelly, polychrome, stepped, tol, watlington,
#           main="Discrete", show.names=FALSE)

# Bivariate
bivcol <- function(pal){
  tit <- substitute(pal)
  pal <- pal()
  ncol <- length(pal)
  nx <- sqrt(length(pal))
  image(matrix(1:ncol, nrow=sqrt(ncol)), axes=FALSE, col=pal)
  mtext(tit)
}
op <- par(mfrow=c(3,4), mar=c(1,1,2,1))
bivcol(stevens.pinkgreen)
bivcol(stevens.bluered)
bivcol(stevens.pinkblue)
bivcol(stevens.greenblue)
bivcol(stevens.purplegold)
bivcol(brewer.orangeblue)
bivcol(brewer.pinkblue)
bivcol(tolochko.redblue)
bivcol(arc.bluepink)
bivcol(census.blueyellow)
```


### HCL from hcl.pals("divergingx")

```{r}

list(
    hcl.colors(n = 11, palette = "Fall"),
    hcl.colors(n = 11, palette = "Geyser"),
    hcl.colors(n = 11, palette = "Berlin"),
    hcl.colors(n = 11, palette = "Zissou 1"),
    hcl.colors(n = 11, palette = "Teal Rose"),
    hcl.colors(n = 11, palette = "Temps")
) %>%
    seecol(., col_brd = "white", lwd_brd = 2, 
           title = "More diverging HCL palettes")
       
```

### Yarrr palettes

```{r}

library(yarrr)
#yarrr::piratepal()

list(
    yarrr::piratepal(palette = "basel"),
    yarrr::piratepal(palette = "appletv"),
    yarrr::piratepal(palette = "espresso"),
    yarrr::piratepal(palette = "info")
) %>% 
    seecol(., col_brd = "white", lwd_brd = 2, 
           title = "Yarrr palettes")

```


### Famous colorblind-friendly palette by Okabe & Ito

```{r}

# The palette with grey:
pal_okabe_ito <- newpal(col = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"),
                        names = c("gray60", "orange", "skyblue", "green", "yellow", "blue", "vermillion", "purple"))
seecol(pal_okabe_ito, hex=TRUE,
       title = "Color-blind friendly color scale (Okabe & Ito, 2002)")
    
# The palette with black:
# cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

### Simple distinct color palette

```{r}

pal_sashat <- newpal(col = c("#e6194B", "#3cb44b", "#ffe119", "#4363d8", "#f58231",
                                "#42d4f4", "#f032e6", "#fabebe", "#469990", "#e6beff",
                                "#9A6324", "#fffac8", "#800000", "#aaffc3", "#000075",
                                "#a9a9a9", "#ffffff", "#000000"),
                        names =c("spanish crimson red", "wagingen green", 
                                 "vivid yellow", "royal blue", "princeton orange", 
                                 "medium turquoise", "razzle dazzle rose", "spanish pink", 
                                 "zomp cyan", "electric lavender", "golden brown", 
                                 "lemon chiffon beige",  "maroon red", "magic mint", 
                                 "navy blue", "dark medium grey", "white", "registration black"))
seecol(pal_sashat, hex=TRUE,
       title = "Simple, distinct color palette")

```

## Create palettes with `visibly`

```{r}

library(visibly)

create_palette("#0058A1", toHCL = TRUE, plot = FALSE)
create_palette("#0058A1", toHCL = TRUE, plot = TRUE)

create_palette("#f2b035", plot = TRUE)

```

```{r}

library(colorspace)

# http://colorspace.r-forge.r-project.org/articles/hclwizard.html

# polarLUV() (= HCL), LUV(), polarLAB(), LAB(), XYZ(), RGB(), sRGB(), HLS(), HSV()

# demo("brewer", package = "colorspace")

demoplot(qualitative_hcl(4, "Dark 3"), type = "lines")
demoplot(sequential_hcl(4, "Viridis"), type = "spine")
demoplot(diverging_hcl(5, "Blue-Red 2"), type = "bar")
demoplot(qualitative_hcl(4, "Set 2"), type = "scatter")

oi <- c("#61A9D9", "#ADD668", "#E6D152", "#CE6BAF", "#797CBA")
swatchplot(
  "-40%" = lighten(oi, 0.4),
  "-20%" = lighten(oi, 0.2),
  "  0%" = oi,
  " 20%" =  darken(oi, 0.2),
  " 40%" =  darken(oi, 0.4),
  off = c(0, 0)
)
```




top selected palettes from other packages

.. continue to source from https://github.com/EmilHvitfeldt/paletteer
   @ line - ghibli

```{r}

# distinct
list(
  c("#F7DC05", "#3d98d3", "#EC0B88", "#5e35b1", "#f9791e", "#3dd378", "#c6c6c6", "#444444"),
  c("#017a4a", "#FFCE4E", "#3d98d3", "#ff363c", "#7559a2", "#794924", "#8cdb5e", "#d6d6d6", "#fb8c00"),
  c("#9F248F", "#FFCE4E", "#017a4a", "#f9791e", "#244579", "#c6242d"),
  c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
) %>% 
    `names<-`(c("primary_awtools", "flat_awtools", "secondary_awtools", "___")) %>%
  seecol()

# continuous
list(
  c("#2A363B", "#019875", "#99B898", "#FECEA8", "#FF847C", "#E84A5F", "#C0392B", "#96281B")
) %>% 
  seecol()

# grey / mono
list(
  c("#d6d6d6", "#adadad", "#707070", "#333333")
) %>% 
  seecol()

# large
c("#c62828", "#f44336", "#9c27b0", "#673ab7", "#3f51b5", "#2196f3", "#29b6f6", "#006064", "#009688", "#4caf50", "#8bc34a", "#ffeb3b", "#ff9800", "#795548", "#9e9e9e", "#607d8b")
c("#e6194B", "#3cb44b", "#ffe119", "#4363d8", "#f58231", "#911eb4", "#42d4f4", "#f032e6", "#bfef45", "#fabebe", "#469990", "#e6beff", "#9A6324", "#fffac8", "#800000", "#aaffc3", "#808000", "#ffd8b1", "#000075", "#a9a9a9", "#ffffff", "#000000")

```





Tableau palettes

https://jrnold.github.io/ggthemes/reference/tableau_color_pal.html

```{r}
tableau_color_pal(palette = "Tableau 10", type = c("regular",
  "ordered-sequential", "ordered-diverging"), direction = 1)
 
```


Shades
https://github.com/jonclayden/shades









```{r}

#786627
#BB611D
#564933

col_vector <- c("#155673", "#B66C1A", "#297b18")
col_vector <- c("#786627", "#564933", "#376A5D", "#BB611D")
col_vector <- c("#264BAC", "#9B2047", "#F1F1F1")
col_vector <- c("#344E3F", "#F0880F", "#1D838A")

col_pos_1 <- col_vector[1]

col_class <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB")
col_coord <- col_class@coords

m1 <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords %>%
  dist(method="euclidean") %>% as.matrix() %>% 
  `colnames<-`(col_vector) %>% 
  `rownames<-`(col_vector) %>%
  reshape2::melt() 

pair_list <- list()
for (i in seq_along(col_vector)) {

  if (i > 1) {
    prev_col <- pair_list[[i - 1]] %>% .[, "Var2"] %>% as.character()
    prev_cols <- pair_list %>% do.call(cbind,. ) %>% 
      .[, "value" != names(.)] %>%
      apply(., 1, unique) %>%
      as.character() %>%
      .[-length(.)]
  }
  
  if (i == 1) {
    pair_list[[i]] <- m1 %>% 
      dplyr::filter(Var1 %in% col_pos_1) %>%
      dplyr::filter(value == max(value)) 
    } else {
      pair_list[[i]] <- m1 %>% 
        dplyr::filter(Var1 %in% prev_col) %>%
        dplyr::filter(!Var2 %in% prev_cols) %>%
        dplyr::filter(value == max(value)) 
      } 
}

pair_list %>% do.call(cbind,. ) %>% 
  .[, "value" != names(.)] %>%
  apply(., 1, unique) %>% 
  seecol()

```



```{r}
library('rwantshue')

col_vector <- c("#155673")
col_coord <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords

col_coord

scheme <- iwanthue(seed = 41, force_init = TRUE)
color_space <- list(
	c(0, 210),	# hue range [0,360]
	c(col_coord[, "C"]-10, col_coord[, "C"]+10),		# chroma range [0,100]
	c(col_coord[, "L"]-10, col_coord[, "L"]+10))		# lightness range [0,100]
palette <- scheme$hex(
	n = 2,
	force_mode = FALSE,
	quality = 100,
	color_space = color_space)

c(col_vector, palette) %>% seecol()

```


hues:
https://github.com/johnbaums/hues
fixed center for kmeans:
https://stackoverflow.com/questions/57933767/k-means-cluster-analysis-in-r-setting-only-one-center-leaving-the-other-center
https://stackoverflow.com/questions/33399000/refitting-clusters-around-fixed-centroids


```{r}



col_vector <- c("#155673")

col_vector <- c("#a83a36")


col_vector <- c("#A60825")


colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords

colorspace::hex2RGB(col_vector) %>%
  as(., "polarLUV") %>% .@coords



c_range <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLUV") %>% .@coords %>% 
    .[, "C"] %>%
    `*`(c(0.6, 1.4))

l_range <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLUV") %>% .@coords %>% 
    .[, "L"] %>%
    `*`(c(0.6, 1.4))


colorspace::hex2RGB(col_vector) %>%
  as(., "LAB") %>% .@coords

n=2

kf <- function(x, clust, nc) {
    cn <- rbind(clust, x[sample(nrow(x), nc-1),])
    kmeans(x, cn)
}

lab <- colorspace::LAB(as.matrix(
    expand.grid(seq(0, 100, 1), seq(-100, 100, 5), seq(-110, 100, 5))))
hcl <- as(lab, 'polarLUV')

hcl_coords <- colorspace::coords(hcl)

hmin=0; hmax=360; cmin=c_range[1]; cmax=c_range[2]; lmin=l_range[1]; lmax=l_range[2]
hcl <- hcl[which(hcl_coords[, 'H'] <= hmax & hcl_coords[, 'H'] >= hmin &
                       hcl_coords[, 'C'] <= cmax & hcl_coords[, 'C'] >= cmin & 
                       hcl_coords[, 'L'] <= lmax & hcl_coords[, 'L'] >= lmin), ]

lab <- lab[which(!is.na(colorspace::hex(lab))), ]



# stats::kmeans(colorspace::coords(lab), n, iter.max=50)


m <- colorspace::coords(lab)

c1 <- c(41, 45, 27)

m_ext <- matrix(rep(c1+0.1, 300000), ncol=3, byrow = TRUE)

m %<>% rbind(., m_ext)


l <- replicate(100, kf(m, c1, 2), simplify=FALSE)
bss <- sapply(l, '[[', "betweenss")
table(signif(bss, 4))

# 538.6 602.5 
#    37    63 
kmo <- l[[which.max(bss)]]

kmo$centers

```

```{r}



col_vector <- c("#155673")

col_vector <- c("#a83a36")


col_vector <- c("#A60825")


colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords

colorspace::hex2RGB(col_vector) %>%
  as(., "polarLUV") %>% .@coords

colorspace::hex2RGB(col_vector) %>%
  as(., "LAB") %>% .@coords


c_range <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords %>% 
    .[, "C"] %>%
    `*`(c(0.6, 1.4))

l_range <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords %>% 
    .[, "L"] %>%
    `*`(c(0.6, 1.4))


colorspace::hex2RGB(col_vector) %>%
  as(., "LAB") %>% .@coords

n=2

kf <- function(x, clust, nc) {
    cn <- rbind(clust, x[sample(nrow(x), nc-1),])
    kmeans(x, cn)
}

lab <- colorspace::LAB(as.matrix(
    expand.grid(seq(0, 100, 1), seq(-100, 100, 5), seq(-110, 100, 5))))
hcl <- as(lab, 'polarLAB')

hcl_coords <- colorspace::coords(hcl)

hmin=0; hmax=360; cmin=c_range[1]; cmax=c_range[2]; lmin=l_range[1]; lmax=l_range[2]
hcl <- hcl[which(hcl_coords[, 'H'] <= hmax & hcl_coords[, 'H'] >= hmin &
                       hcl_coords[, 'C'] <= cmax & hcl_coords[, 'C'] >= cmin & 
                       hcl_coords[, 'L'] <= lmax & hcl_coords[, 'L'] >= lmin), ]

lab <- as(hcl, 'LAB')    
lab <- lab[which(!is.na(colorspace::hex(lab))), ]



# stats::kmeans(colorspace::coords(lab), n, iter.max=50)


m <- colorspace::coords(lab)

c1 <- c(34, -9, -22)

m_ext <- matrix(rep(c1+0.1, 100000), ncol=3, byrow = TRUE)

m %<>% rbind(., m_ext)


l <- replicate(100, kf(m, c1, 2), simplify=FALSE)
bss <- sapply(l, '[[', "betweenss")
table(signif(bss, 4))

# 538.6 602.5 
#    37    63 
kmo <- l[[which.max(bss)]]

kmo$centers

```


```{r}

library("plot3D")
scatter3D(x=m[,1], y=m[,2], z=m[,3])

```





RWantsHue
https://medialab.github.io/iwanthue/
https://medialab.github.io/iwanthue/examples/



https://learnui.design/tools/data-color-picker.html

https://projects.susielu.com/viz-palette


```{r rwantshue, eval = FALSE}

library('rwantshue')

# create a color scheme object
scheme <- iwanthue() # get the iwanthue singleton
scheme <- iwanthue(seed = 42, force_init = TRUE) # recreate with a seed

# generate a new color palette (vector of hex values) with presets...
scheme$hex(10)
scheme$hex(10, color_space = hcl_presets$fluo)

# ... or make custom adjustments:
color_space <- list(
	c(330, 360),	# hue range [0,360]
	c(0, 100),		# chroma range [0,100]
	c(0, 100))		# lightness range [0,100]
palette <- scheme$hex(
	n = 8,
	force_mode = FALSE,
	quality = 50,
	color_space = color_space)
	
# use it in a plot
plot(1:8, col = scheme$hex(8), pch = 16, cex = 10)

# You can also fetch a rgb matrix
scheme$rgb(8)


```









