---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.pos = 'H')

library(magrittr)
library(ggplot2)

library(colorspace)
library(pals)
library(scales)
library(unikn)


# forces a line before and after each plot
# https://stackoverflow.com/questions/37030219/r-markdown-plots-within-a-loop-going-out-of-margin-when-typesetting-to-pdf
my_plot_hook <- function(x, options)
  paste("\n", knitr::hook_plot_tex(x, options), "\n")
knitr::knit_hooks$set(plot = my_plot_hook)

fig1_url <- "http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/figure/unnamed-chunk-7-1.png"

```

# Theory

ggplot2:
By default, the colors for discrete scales are evenly spaced around a HSL color circle. For example, if there are two colors, then they will be selected from opposite points on the circle; if there are three colors, they will be 120? apart on the color circle; and so on. The colors used for different numbers of levels are shown here:

<center><img src="`r fig1_url`"></center>

OR

![](`r fig1_url`)

Some other interseting literature and tools

http://vis.stanford.edu/color-names/analyzer/



# Color Palettes


## Most Common Palettes


### HCL palettes

http://colorspace.r-forge.r-project.org/articles/hcl_palettes.html


```{r}

# HCL palettes
hcl.pals()
colorspace::hcl_palettes()

colorspace::hcl_palettes("qualitative", n = 7, plot = TRUE)
colorspace::hcl_palettes("sequential (single-hue)", n = 7, plot = TRUE)
colorspace::hcl_palettes("sequential (multi-hue)", n = 7, plot = TRUE)
colorspace::hcl_palettes("diverging", n = 7, plot = TRUE)

```

### ColorBrewer Palettes

```{r}

# RColorBrewer
# RColorBrewer::display.brewer.all()


rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "qual"] %>% 
    `names<-`(paste0("pal", 1:length(.)))
RColorBrewer::brewer.pal.info %>% 
  .[.$category == "qual", ] %>%
    tibble::rownames_to_column(var = "palette") %>%
    apply(., 1, function (x) {
        n <- as.numeric(x["maxcolors"])
        pal_name <- as.character(x["palette"]) 
        RColorBrewer::brewer.pal(n, pal_name) %>% usecol() %>% 
            `comment<-`(paste(pal_name))
    }) %>% 
    `names<-`(rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "qual"]) %>%
    unikn::seecol(., col_brd = "white", lwd_brd = 4, 
                  title = "ColorBrewer palettes - qualitative")


rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "seq"] %>% 
    `names<-`(paste0("pal", 1:length(.)))
RColorBrewer::brewer.pal.info %>% 
  .[.$category == "seq", ] %>%
    tibble::rownames_to_column(var = "palette") %>%
    apply(., 1, function (x) {
        n <- as.numeric(x["maxcolors"])
        pal_name <- as.character(x["palette"]) 
        RColorBrewer::brewer.pal(n, pal_name) %>% usecol() %>% 
            `comment<-`(paste(pal_name))
    }) %>% t() %>% split(1:nrow(.)) %>%
    `names<-`(rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "seq"]) %>%
    unikn::seecol(., col_brd = "white", lwd_brd = 4, 
                  title = "ColorBrewer palettes - sequential")

rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "div"] %>% 
    `names<-`(paste0("pal", 1:length(.)))
RColorBrewer::brewer.pal.info %>% 
  .[.$category == "div", ] %>%
    tibble::rownames_to_column(var = "palette") %>%
    apply(., 1, function (x) {
        n <- as.numeric(x["maxcolors"])
        pal_name <- as.character(x["palette"]) 
        RColorBrewer::brewer.pal(n, pal_name) 
    }) %>% t() %>% split(1:nrow(.)) %>%
    `names<-`(rownames(RColorBrewer::brewer.pal.info)[RColorBrewer::brewer.pal.info$category == "div"]) %>%
    unikn::seecol(., col_brd = "white", lwd_brd = 4, 
                  title = "ColorBrewer palettes - divergent")
```

### Viridis Palettes

Viridis palettes are included in HCL palettes

```{r, eval=FALSE}

# Viridis
library(viridis)
c1 <- viridis(12)
c2 <- magma(12)
c3 <- inferno(12)
c4 <- plasma(12)
c5 <- cividis(12)
unikn::seecol(list(c1, c2, c3, c4, c5), col_brd = "white", lwd_brd = 4,
title = "Various viridis color palettes (n = 20)")

```

### ggthemes palettes

```{r}

ggthemes::ggthemes_data %>% names()

pal_name <- "solarized"

tmp <- ggthemes::ggthemes_data %>% .[[pal_name]] %>% lapply(., "[", "value") %>% lapply(is.data.frame) %>% unlist()
ggthemes::ggthemes_data %>% .[[pal_name]] %>% lapply(., "[", "value") %>% .[tmp] %>% lapply(t) %>% 
    seecol(title = paste0("ggthemes ", pal_name, " palettes"))


pal_name <- "ptol"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% .[[1]] %>%
    seecol(title = paste0("ggthemes ", pal_name, " palettes"))

pal_name <- "calc"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% .[["colors"]] %>% .$value %>%
    seecol(title = paste0("ggthemes ", pal_name, " palettes"))


pal_name <- "tableau"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% .$'color-palettes' %>% 
    .$regular %>% lapply("[", "value") %>% lapply(t) %>% 
    seecol(title = paste0("ggthemes ", pal_name, " regular palettes"))

ggthemes::ggthemes_data %>% .[[pal_name]] %>% .$'color-palettes' %>% 
    .$'ordered-diverging' %>% lapply("[", "value") %>% lapply(t) %>% 
    seecol(title = paste0("ggthemes ", pal_name, " ordered-diverging palettes"))


ggthemes::ggthemes_data %>% .[[pal_name]] %>% .$'color-palettes' %>% 
    .$'ordered-sequential' %>% lapply("[", "value") %>% lapply(t) %>% 
    seecol(title = paste0("ggthemes ", pal_name, " ordered-sequential palette"))


pal_name <- "few"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% .$colors %>%
    lapply("[", "value") %>% lapply(t) %>% 
    seecol(title = paste0("ggthemes ", pal_name, " palette"))

pal_name <- "manyeyes"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% 
    seecol(title = paste0("ggthemes ", pal_name, " palette"))

pal_name <- "gdocs"
ggthemes::ggthemes_data %>% .[[pal_name]] %>% .$colors %>%
    seecol(title = paste0("ggthemes ", pal_name, " palette"))



```


### ggsci palettes

```{r}

library(ggsci)

c("NPG", "AAAS", "NEJM", "Lancet", "JAMA", "JCO", "LocusZoom") %>%
    `names<-`(paste0("pal", 1:length(.)))

list(
    pal_npg("nrc")(10),
    pal_aaas("default")(10),
    pal_nejm("default")(8),
    pal_lancet("lanonc")(9),
    pal_jama("default")(7),
    pal_jco("default")(10),
    pal_locuszoom("default")(7)
) %>%
    seecol(., col_brd = "white", lwd_brd = 2, 
           title = "ggsci palettes")


c("D3.20", "D3.20b",  "D3.20c") %>%
    `names<-`(c("pal1-2", "pal3-6", "pal7-11"))

list(
    pal_d3("category20")(20)[1:10],
    pal_d3("category20")(20)[11:20],
    pal_d3("category20b")(20)[1:5],
    pal_d3("category20b")(20)[6:10],
    pal_d3("category20b")(20)[11:15],
    pal_d3("category20b")(20)[16:20],
    pal_d3("category20c")(20)[1:5],
    pal_d3("category20c")(20)[6:10],
    pal_d3("category20c")(20)[11:15],
    pal_d3("category20c")(20)[16:20]
) %>%
    seecol(., col_brd = "white", lwd_brd = 2, 
           title = "ggsci D3 palettes")

```


### pals bivariate palettes

```{r}

# Discrete
# pal.bands(alphabet, alphabet2, cols25, glasbey, kelly, polychrome, stepped, tol, watlington,
#           main="Discrete", show.names=FALSE)

# Bivariate
bivcol <- function(pal){
  tit <- substitute(pal)
  pal <- pal()
  ncol <- length(pal)
  nx <- sqrt(length(pal))
  image(matrix(1:ncol, nrow=sqrt(ncol)), axes=FALSE, col=pal)
  mtext(tit)
}
op <- par(mfrow=c(3,4), mar=c(1,1,2,1))
bivcol(stevens.pinkgreen)
bivcol(stevens.bluered)
bivcol(stevens.pinkblue)
bivcol(stevens.greenblue)
bivcol(stevens.purplegold)
bivcol(brewer.orangeblue)
bivcol(brewer.pinkblue)
bivcol(tolochko.redblue)
bivcol(arc.bluepink)
bivcol(census.blueyellow)
```


### HCL from hcl.pals("divergingx")

```{r}

list(
    hcl.colors(n = 11, palette = "Fall"),
    hcl.colors(n = 11, palette = "Geyser"),
    hcl.colors(n = 11, palette = "Berlin"),
    hcl.colors(n = 11, palette = "Zissou 1"),
    hcl.colors(n = 11, palette = "Teal Rose"),
    hcl.colors(n = 11, palette = "Temps")
) %>%
    seecol(., col_brd = "white", lwd_brd = 2, 
           title = "More diverging HCL palettes")
       
```

### Yarrr palettes

```{r}

library(yarrr)
#yarrr::piratepal()

list(
    yarrr::piratepal(palette = "basel"),
    yarrr::piratepal(palette = "appletv"),
    yarrr::piratepal(palette = "espresso"),
    yarrr::piratepal(palette = "info")
) %>% 
    seecol(., col_brd = "white", lwd_brd = 2, 
           title = "Yarrr palettes")

```


### Famous colorblind-friendly palette by Okabe & Ito

```{r}

# The palette with grey:
pal_okabe_ito <- newpal(col = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"),
                        names = c("gray60", "orange", "skyblue", "green", "yellow", "blue", "vermillion", "purple"))
seecol(pal_okabe_ito, hex=TRUE,
       title = "Color-blind friendly color scale (Okabe & Ito, 2002)")
    
# The palette with black:
# cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

### Simple distinct color palette

```{r}

pal_sashat <- newpal(col = c("#e6194B", "#3cb44b", "#ffe119", "#4363d8", "#f58231",
                                "#42d4f4", "#f032e6", "#fabebe", "#469990", "#e6beff",
                                "#9A6324", "#fffac8", "#800000", "#aaffc3", "#000075",
                                "#a9a9a9", "#ffffff", "#000000"),
                        names =c("spanish crimson red", "wagingen green", 
                                 "vivid yellow", "royal blue", "princeton orange", 
                                 "medium turquoise", "razzle dazzle rose", "spanish pink", 
                                 "zomp cyan", "electric lavender", "golden brown", 
                                 "lemon chiffon beige",  "maroon red", "magic mint", 
                                 "navy blue", "dark medium grey", "white", "registration black"))
seecol(pal_sashat, hex=TRUE,
       title = "Simple, distinct color palette")

```

## Create palettes with `visibly`

```{r}

library(visibly)


create_palette("#0058A1", plot = FALSE)
create_palette("#0058A1", toHCL = TRUE, plot = TRUE)

create_palette("#f2b035", plot = TRUE)

```

```{r}

library(colorspace)

# http://colorspace.r-forge.r-project.org/articles/hclwizard.html

# polarLUV() (= HCL), LUV(), polarLAB(), LAB(), XYZ(), RGB(), sRGB(), HLS(), HSV()

# demo("brewer", package = "colorspace")

demoplot(qualitative_hcl(4, "Dark 3"), type = "lines")
demoplot(sequential_hcl(4, "Viridis"), type = "spine")
demoplot(diverging_hcl(5, "Blue-Red 2"), type = "bar")
demoplot(qualitative_hcl(4, "Set 2"), type = "scatter")

oi <- c("#61A9D9", "#ADD668", "#E6D152", "#CE6BAF", "#797CBA")
swatchplot(
  "-40%" = lighten(oi, 0.4),
  "-20%" = lighten(oi, 0.2),
  "  0%" = oi,
  " 20%" =  darken(oi, 0.2),
  " 40%" =  darken(oi, 0.4),
  off = c(0, 0)
)
```


## Tol Color Schemes

```{r}

cols <- inlmisc::GetTolColors(n = 10)
print(cols)
plot(cols)

op <- graphics::par(mfrow = c(6, 1), oma = c(0, 0, 0, 0))
plot(inlmisc::GetTolColors(7, scheme = "bright"))
plot(inlmisc::GetTolColors(7, scheme = "vibrant"))
plot(inlmisc::GetTolColors(9, scheme = "muted"))
plot(inlmisc::GetTolColors(6, scheme = "pale"))
plot(inlmisc::GetTolColors(6, scheme = "dark"))
plot(inlmisc::GetTolColors(9, scheme = "light"))
graphics::par(op)


# function also adopted by ggthemes
ggthemes::ptol_pal()(5) %>% seecol()


```



top selected palettes from other packages

.. continue to source from https://github.com/EmilHvitfeldt/paletteer
   @ line - ghibli

```{r}

# distinct
list(
  c("#F7DC05", "#3d98d3", "#EC0B88", "#5e35b1", "#f9791e", "#3dd378", "#c6c6c6", "#444444"),
  c("#017a4a", "#FFCE4E", "#3d98d3", "#ff363c", "#7559a2", "#794924", "#8cdb5e", "#d6d6d6", "#fb8c00"),
  c("#9F248F", "#FFCE4E", "#017a4a", "#f9791e", "#244579", "#c6242d"),
  c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
) %>% 
    `names<-`(c("primary_awtools", "flat_awtools", "secondary_awtools", "___")) %>%
  seecol()

# continuous
list(
  c("#2A363B", "#019875", "#99B898", "#FECEA8", "#FF847C", "#E84A5F", "#C0392B", "#96281B")
) %>% 
  seecol()

# grey / mono
list(
  c("#d6d6d6", "#adadad", "#707070", "#333333")
) %>% 
  seecol()

# large
c("#c62828", "#f44336", "#9c27b0", "#673ab7", "#3f51b5", "#2196f3", "#29b6f6", "#006064", "#009688", "#4caf50", "#8bc34a", "#ffeb3b", "#ff9800", "#795548", "#9e9e9e", "#607d8b")
c("#e6194B", "#3cb44b", "#ffe119", "#4363d8", "#f58231", "#911eb4", "#42d4f4", "#f032e6", "#bfef45", "#fabebe", "#469990", "#e6beff", "#9A6324", "#fffac8", "#800000", "#aaffc3", "#808000", "#ffd8b1", "#000075", "#a9a9a9", "#ffffff", "#000000")

```





Tableau palettes

https://jrnold.github.io/ggthemes/reference/tableau_color_pal.html

```{r}
tableau_color_pal(palette = "Tableau 10", type = c("regular",
  "ordered-sequential", "ordered-diverging"), direction = 1)
 
```


Shades
https://github.com/jonclayden/shades



ggthemes

Has collection of canva.com palettes:
https://www.canva.com/learn/100-color-combinations/

List: http://makeadifferencewithdata.com/wp-content/uploads/2016/12/color-palettes.txt


```{r}


show_col(canva_pal("Fresh and bright")(4))
show_col(canva_pal("Subdued and proffesional")(4))


```






```{r}

#786627
#BB611D
#564933

col_vector <- c("#155673", "#B66C1A", "#297b18")
col_vector <- c("#786627", "#564933", "#376A5D", "#BB611D")
col_vector <- c("#264BAC", "#9B2047", "#F1F1F1")
col_vector <- c("#344E3F", "#F0880F", "#1D838A")

col_pos_1 <- col_vector[1]

col_class <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB")
col_coord <- col_class@coords

m1 <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords %>%
  dist(method="euclidean") %>% as.matrix() %>% 
  `colnames<-`(col_vector) %>% 
  `rownames<-`(col_vector) %>%
  reshape2::melt() 

pair_list <- list()
for (i in seq_along(col_vector)) {

  if (i > 1) {
    prev_col <- pair_list[[i - 1]] %>% .[, "Var2"] %>% as.character()
    prev_cols <- pair_list %>% do.call(cbind,. ) %>% 
      .[, "value" != names(.)] %>%
      apply(., 1, unique) %>%
      as.character() %>%
      .[-length(.)]
  }
  
  if (i == 1) {
    pair_list[[i]] <- m1 %>% 
      dplyr::filter(Var1 %in% col_pos_1) %>%
      dplyr::filter(value == max(value)) 
    } else {
      pair_list[[i]] <- m1 %>% 
        dplyr::filter(Var1 %in% prev_col) %>%
        dplyr::filter(!Var2 %in% prev_cols) %>%
        dplyr::filter(value == max(value)) 
      } 
}

pair_list %>% do.call(cbind,. ) %>% 
  .[, "value" != names(.)] %>%
  apply(., 1, unique) %>% 
  seecol()

```



```{r}
library('rwantshue')

col_vector <- c("#155673")
col_coord <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords

col_coord

scheme <- iwanthue(seed = 41, force_init = TRUE)
color_space <- list(
	c(0, 210),	# hue range [0,360]
	c(col_coord[, "C"]-10, col_coord[, "C"]+10),		# chroma range [0,100]
	c(col_coord[, "L"]-10, col_coord[, "L"]+10))		# lightness range [0,100]
palette <- scheme$hex(
	n = 2,
	force_mode = FALSE,
	quality = 100,
	color_space = color_space)

c(col_vector, palette) %>% seecol()

```


hues:
https://github.com/johnbaums/hues
fixed center for kmeans:
https://stackoverflow.com/questions/57933767/k-means-cluster-analysis-in-r-setting-only-one-center-leaving-the-other-center
https://stackoverflow.com/questions/33399000/refitting-clusters-around-fixed-centroids


```{r}



col_vector <- c("#155673")

col_vector <- c("#a83a36")


col_vector <- c("#A60825")


colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords

colorspace::hex2RGB(col_vector) %>%
  as(., "polarLUV") %>% .@coords



c_range <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLUV") %>% .@coords %>% 
    .[, "C"] %>%
    `*`(c(0.6, 1.4))

l_range <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLUV") %>% .@coords %>% 
    .[, "L"] %>%
    `*`(c(0.6, 1.4))


colorspace::hex2RGB(col_vector) %>%
  as(., "LAB") %>% .@coords

n=2

kf <- function(x, clust, nc) {
    cn <- rbind(clust, x[sample(nrow(x), nc-1),])
    kmeans(x, cn)
}

lab <- colorspace::LAB(as.matrix(
    expand.grid(seq(0, 100, 1), seq(-100, 100, 5), seq(-110, 100, 5))))
hcl <- as(lab, 'polarLUV')

hcl_coords <- colorspace::coords(hcl)

hmin=0; hmax=360; cmin=c_range[1]; cmax=c_range[2]; lmin=l_range[1]; lmax=l_range[2]
hcl <- hcl[which(hcl_coords[, 'H'] <= hmax & hcl_coords[, 'H'] >= hmin &
                       hcl_coords[, 'C'] <= cmax & hcl_coords[, 'C'] >= cmin & 
                       hcl_coords[, 'L'] <= lmax & hcl_coords[, 'L'] >= lmin), ]

lab <- lab[which(!is.na(colorspace::hex(lab))), ]



# stats::kmeans(colorspace::coords(lab), n, iter.max=50)


m <- colorspace::coords(lab)

c1 <- c(41, 45, 27)

m_ext <- matrix(rep(c1+0.1, 300000), ncol=3, byrow = TRUE)

m %<>% rbind(., m_ext)


l <- replicate(100, kf(m, c1, 2), simplify=FALSE)
bss <- sapply(l, '[[', "betweenss")
table(signif(bss, 4))

# 538.6 602.5 
#    37    63 
kmo <- l[[which.max(bss)]]

kmo$centers

```

```{r}



col_vector <- c("#155673")

col_vector <- c("#a83a36")


col_vector <- c("#A60825")


colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords

colorspace::hex2RGB(col_vector) %>%
  as(., "polarLUV") %>% .@coords

colorspace::hex2RGB(col_vector) %>%
  as(., "LAB") %>% .@coords


c_range <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords %>% 
    .[, "C"] %>%
    `*`(c(0.6, 1.4))

l_range <- colorspace::hex2RGB(col_vector) %>%
  as(., "polarLAB") %>% .@coords %>% 
    .[, "L"] %>%
    `*`(c(0.6, 1.4))


colorspace::hex2RGB(col_vector) %>%
  as(., "LAB") %>% .@coords

n=2

kf <- function(x, clust, nc) {
    cn <- rbind(clust, x[sample(nrow(x), nc-1),])
    kmeans(x, cn)
}

lab <- colorspace::LAB(as.matrix(
    expand.grid(seq(0, 100, 1), seq(-100, 100, 5), seq(-110, 100, 5))))
hcl <- as(lab, 'polarLAB')

hcl_coords <- colorspace::coords(hcl)

hmin=0; hmax=360; cmin=c_range[1]; cmax=c_range[2]; lmin=l_range[1]; lmax=l_range[2]
hcl <- hcl[which(hcl_coords[, 'H'] <= hmax & hcl_coords[, 'H'] >= hmin &
                       hcl_coords[, 'C'] <= cmax & hcl_coords[, 'C'] >= cmin & 
                       hcl_coords[, 'L'] <= lmax & hcl_coords[, 'L'] >= lmin), ]

lab <- as(hcl, 'LAB')    
lab <- lab[which(!is.na(colorspace::hex(lab))), ]



# stats::kmeans(colorspace::coords(lab), n, iter.max=50)


m <- colorspace::coords(lab)

c1 <- c(34, -9, -22)

m_ext <- matrix(rep(c1+0.1, 100000), ncol=3, byrow = TRUE)

m %<>% rbind(., m_ext)


l <- replicate(100, kf(m, c1, 2), simplify=FALSE)
bss <- sapply(l, '[[', "betweenss")
table(signif(bss, 4))

# 538.6 602.5 
#    37    63 
kmo <- l[[which.max(bss)]]

kmo$centers

```


```{r}

library("plot3D")
scatter3D(x=m[,1], y=m[,2], z=m[,3])

```





RWantsHue
https://medialab.github.io/iwanthue/
https://medialab.github.io/iwanthue/examples/




```{r rwantshue, eval = FALSE}

library('rwantshue')

# create a color scheme object
scheme <- iwanthue() # get the iwanthue singleton
scheme <- iwanthue(seed = 42, force_init = TRUE) # recreate with a seed

# generate a new color palette (vector of hex values) with presets...
scheme$hex(10)
scheme$hex(10, color_space = hcl_presets$fluo)

# ... or make custom adjustments:
color_space <- list(
	c(330, 360),	# hue range [0,360]
	c(0, 100),		# chroma range [0,100]
	c(0, 100))		# lightness range [0,100]
palette <- scheme$hex(
	n = 8,
	force_mode = FALSE,
	quality = 50,
	color_space = color_space)
	
# use it in a plot
plot(1:8, col = scheme$hex(8), pch = 16, cex = 10)

# You can also fetch a rgb matrix
scheme$rgb(8)


```









