---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

library(magrittr)
library(ggplot2)
library(colorspace)
library(unikn)

```


## Creating a custom palette

1. Selected 2-3 main theme colors: jpr_theme, acs_theme
2. Selected extended color palette from HP and sorted in IWantHue by diff


```{r}

# jpr_colors <- read.csv("../Dropbox/jpr_palette.csv", stringsAsFactors = FALSE)
(theme_colors <- read.csv("../Dropbox/proteomics_palette.csv", stringsAsFactors = FALSE))

list(
    theme_colors[1:3, 1],
    theme_colors[1:5, 2],
    theme_colors[1:5, 3]
) %>% 
    seecol(title = "Proteomics Journal theme colors")

```

#### IWantHue generated palette

- Select 5 color palette and manually pick first colors from the theme.
- Adjust C and L around the values of selected colors
- Reroll palette and sort by difference

```{r, eval=FALSE}

# select HCL values here:
colorspace::choose_color()

```


```{r}

# C and L ranges based on 2 or more base theme colors 
# HCL values from IWH
c1 <- 27
c2 <- 75   #bring C closer to first color's C 
(c1+c2)/2 - 22.5; (c1+c2)/2 + 22.5

l1 <- 32
l2 <- 31
(l1+l2)/2 - 22.5; (l1+l2)/2 + 22.5


c1 <- 26
c2 <- 36
(c1+c2)/2 - 22.5; (c1+c2)/2 + 22.5

l1 <- 33
l2 <- 59
(l1+l2)/2 - 22.5; (l1+l2)/2 + 22.5

list(
    c("#005274", "#8C1843"),  # first color, second with adjusted C (max dist ~10)
    c("#005274", "#94434e"),  # first color + partner
    c("#8C1843", "#63672c"),  # second color + partner
    c("#005274", "#8C1843", "#656628"),  # 3 and more color palettes sorted by difference (1st color fixed)
    c("#005274", "#8C1843", "#656628", "#6b4091"),
    c("#005274", "#8C1843", "#656628", "#57449d", "#893a7d"), 
    
    c("#005274", "#cc777c"),
    c("#005274", "#8c6c56"),
    c("#cc777c", "#6a7e79"),
    c("#005274", "#cc777c", "#836197"),
    c("#005274", "#cc777c", "#6b794a", "#836197"),
    c("#005274", "#cc777c", "#5c8257", "#836197", "#8a5f36"),
    
    theme_colors[1:5, 3] #should be ordered in IWH
) %>% {. ->> custom_qual_palette } %>%
    seecol(title = "`I Want Hue` generated palettes")

# create_palette("#1851a4", plot = FALSE) %>% 
#   seecol(title = "Colors relative to initial color according to color wheel theory")


```


Diverging palette

Method 1:
1: use 2 complementary colors (eg. blue/red) from previously defined qulitative palette 
 and let hcl_diverging function do the scaling
2: use 1 color and select second color in IWH 
    2a: using C and L space similar to the first color
    2b: using default IWH settings


```{r, eval=FALSE}

# select HCL values here:
colorspace::choose_color()

```


```{r}

#005274   blue from previously defined qualitative palette
hcl_1 <- c(237, 40, 32)   # in IWH 253, 27, 32
#8C1843   red from previously defined qualitative palette
hcl_2 <- c(358, 72, 31)

#822b45   red  IWH: H 6+/-10, C 40+/-5,  L 32+/-3
hcl_3 <- c(358, 56, 32)
#852f3b   red  IWH: H 6+/-30, C 40+/-15,  L 32+/-10
hcl_4 <- c(7, 59, 33)

#765845   complementary to blue  IWH default settings
hcl_5 <- c(39, 27, 40)


newpal(col = c("#005274", "#8C1843", "#FFFFFF", 
               "#005274", "#9E2945", "#FFFFFF",
               "#005274", "#9D2F38", "#FFFFFF",
               "#005274", "#aa8852"),
       names = c("dark imperial blue", "pansy purple", " ",
                 "dark imperial blue", "solid pink", " ",
                 "dark imperial blue", "solid pink 2", " ",
                 "dark imperial blue", "tuscan red"
                 )) %>% 
  seecol(rgb=FALSE, title = "Color pairs for diverging gradients")


# examples for predefined palettes
#colorspace::hcl_palettes("diverging", n = 7, plot = F) %>% as.data.frame()

l_max = 90


list(
    colorspace::diverging_hcl(n=11, h1=hcl_1[1], h2=hcl_2[1], 
                                  cmax = (hcl_1[2]+hcl_2[2])/2, 
                                  l1=min(hcl_1[3], hcl_2[3]), 
                                  l2=l_max, p1=1.0),
    colorspace::diverging_hcl(n=11, h1=hcl_1[1], h2=hcl_2[1], 
                                  cmax = (hcl_1[2]+hcl_2[2])/2, 
                                  l1=min(hcl_1[3], hcl_2[3]), 
                                  l2=l_max, p1=1.5),
    colorspace::diverging_hcl(n=11, h1=hcl_1[1], h2=hcl_3[1], 
                                  cmax = (hcl_1[2]+hcl_3[2])/2, 
                                  l1=min(hcl_1[3], hcl_3[3]), 
                                  l2=l_max, p1=1.0),
    colorspace::diverging_hcl(n=11, h1=hcl_1[1], h2=hcl_3[1], 
                                  cmax = (hcl_1[2]+hcl_3[2])/2, 
                                  l1=min(hcl_1[3], hcl_3[3]), 
                                  l2=l_max, p1=1.5),
    colorspace::diverging_hcl(n=11, h1=hcl_1[1], h2=hcl_4[1], 
                                  cmax = (hcl_1[2]+hcl_4[2])/2, 
                                  l1=min(hcl_1[3], hcl_4[3]), 
                                  l2=l_max, p1=1.0),
    colorspace::diverging_hcl(n=11, h1=hcl_1[1], h2=hcl_4[1], 
                                  cmax = (hcl_1[2]+hcl_4[2])/2, 
                                  l1=min(hcl_1[3], hcl_4[3]), 
                                  l2=l_max, p1=1.5),
    colorspace::diverging_hcl(n=11, h1=hcl_1[1], h2=hcl_5[1], 
                                  cmax = (hcl_1[2]+hcl_5[2])/2, 
                                  l1=min(hcl_1[3], hcl_5[3]), 
                                  l2=l_max, p1=1.0),
    colorspace::diverging_hcl(n=11, h1=hcl_1[1], h2=hcl_5[1], 
                                  cmax = (hcl_1[2]+hcl_5[2])/2, 
                                  l1=min(hcl_1[3], hcl_5[3]), 
                                  l2=l_max, p1=1.5)
) %>% {. ->> custom_div_palette_1 } %>%
  seecol()
```

Method 2:
1: use 2 complementary colors (eg. blue/red) from previously defined qulitative palette 
 and let scale logically
 1a: using mean C and L from both colors as starting points
 1b: using max C and min L from both  colors as starting points
    

```{r}

#blue
hcl_1
#red
hcl_2


n <- 11
l_max <- 90
h_grey <- 94


### a: scaling from/to mean C and L values
c_seq_a <- seq(mean(c(hcl_1[2], hcl_2[2])), 0, 
               by = -1 * mean(c(hcl_1[2], hcl_2[2])) / floor(n/2))
l_seq_a <- seq(mean(c(hcl_1[3], hcl_2[3])), l_max, 
               by = (l_max - mean(hcl_1[3], hcl_2[3])) / floor(n/2))

### b: scaling from/to max C and min L values
c_seq_b <- seq( max(hcl_1[2], hcl_2[2]), 0, 
                by = -1 * max(hcl_1[2], hcl_2[2]) / floor(n/2))
l_seq_b <- seq( min(hcl_1[3], hcl_2[3]), l_max, 
                by = (l_max - min(hcl_1[3], hcl_2[3])) / floor(n/2))


color1 <- cbind(hcl_1[1], c_seq_a, l_seq_a)
#color1[1, ] <- hcl_1
color1[dim(color1)[1], ] <- c(h_grey, 0, l_max)
color2 <- cbind(hcl_2[1], c_seq_a, l_seq_a)
#color2[1, ] <- hcl_2
color2[dim(color2)[1], ] <- c(h_grey, 0, l_max)
my_gradient_a <- rbind(color1, color2 %>% apply(., 2, rev) %>% .[-1, ]) %>%
    `colnames<-`(c("H", "C", "L"))

color1 <- cbind(hcl_1[1], c_seq_b, l_seq_b)
#color1[1, ] <- hcl_1
color1[dim(color1)[1], ] <- c(h_grey, 0, l_max)
color2 <- cbind(hcl_2[1], c_seq_b, l_seq_b)
#color2[1, ] <- hcl_2
color2[dim(color2)[1], ] <- c(h_grey, 0, l_max)
my_gradient_b <- rbind(color1, color2 %>% apply(., 2, rev) %>% .[-1, ]) %>%
    `colnames<-`(c("H", "C", "L"))

list(
    my_gradient_a %>% apply(., 1, function (x) hcl(x[1], x[2], x[3])), 
    my_gradient_b %>% apply(., 1, function (x) hcl(x[1], x[2], x[3]))
) %>%
    {. ->> custom_div_palette_2} %>%
    seecol()

```

All gradients combined

```{r}

c(custom_qual_palette,
  custom_div_palette_2,
  custom_div_palette_1) %>% 
  {. ->> custom_div_palette} %>%
  seecol()

```

